%!TEX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
 
\makeatletter
\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
\makeatother

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kunal}{Ghosh}{ \urlstyle{same}
\href{mailto:kunal.t2@gmail.com}{kunal.t2@gmail.com} | +358-0465645531 | github.com/kunalghosh
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Masters}
Machine Learning and Data Mining\\
Aalto School of Science\\
Grade - 4.42\\
\location{Graduation 2017 Tentative}
\sectionsep

\subsection{Undergraduate}
Computer Science\\
Visvesvaraya Technological University\\
\location{Grad May 2011 | Bangalore, India}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Masters}
\textbullet{} Special Course on Deep Learning\\
\textbullet{} Programming Parallel Computers \\
\textbullet{} Information Retrieval
\textbullet{} Bayesian Data Analysis\\
\textbullet{} Machine Learning \& Neural Networks\\
\textbullet{} Machine Learning Basic Principles\\
\textbullet{} Algorithmic Methods of Data Mining\\
\textbullet{} Computational Science \\
\sectionsep

\subsection{MOOC}
\location{Learning From Data (edX.org):}
\textbullet{} Instructor : Prof Yaser (Caltech)\\
\textbullet{} 10 week long Machine Learning course with 8 homework sets and \\a final exam
\textbullet{} Assignments done using \\ \textbf{Matlab and LibSVM}\\
\textbullet{} Course with significant theoretical content. Topics include : Theory of Generalization, VC Dimensions, Kernel Methods and SVM
\textbullet{} Grade: 80\%

\sectionsep
\location{Machine Learning (Coursera):}
\textbullet{} Instructor : Prof Andrew (Stanford)\\
\textbullet{} 10 week long course.\\
\textbullet{} Assignments done in \textbf{Octave}.\\
\textbullet{} Practical course focusing more on applications of machine learning.\\
\textbullet{} Grade: 100\%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Full Professional Proficiency:}
Python (Including Numpy, Scipy, SciKit Learn) \textbullet{}   Java  \textbullet{} Shell \\
\sectionsep
\location{Working Proficiency:}
\textbullet{} \textbf{Theano} \textbullet{} C \textbullet{} C++ (Cuda \& OpenMP) \textbullet{} Stan (Probabilistic Programming) \textbullet{} Matlab \& Octave \textbullet{} SQL\\
\sectionsep
\location{Familiar:}
Javascript \textbullet{} Assembly \textbullet{} CSS \textbullet{} \LaTeX\ \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Amazon}
\descript{| Software Development Engineering in Test }
\location{Dec 2013 - Aug 2015 | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Significant Contribution : Developed tests to validate the effect of seasonality on an Shoe size recommendation system which uses customer purchases to make predictions. Implemented using \textbf{Java}.
\end{tightemize}
\sectionsep

\runsubsection{Amazon}
\descript{| Quality Assurance Engineer }
\location{Aug 2011 – Nov 2013 | Bangalore, India}
\begin{tightemize}
\item Developed a system to automatically detect UI defects (text overlaps, element mis-alignments etc) in Amazon retail websites. It was developed using \textbf{Python} and \textbf{“Image Magick”}.
\item Implemented a log processing system to identify new Errors/Fatals in website logs. Developed using \textbf{Python} and \textbf{Amazon internal tools for distributed job scheduling}.
\end{tightemize}
\sectionsep

\runsubsection{OwnCloud.org}
\descript{| Google Summer of Code Intern }
\location{May 2011 – Aug 2011}
\begin{tightemize}
\item Implemented a prototype file synchronization system for OwnCloud. Implemented the SyncML server component in PhP and a prototype desktop client using the Funambol SyncML SDK.
\end{tightemize}
\sectionsep

\runsubsection{DigiKam.org}
\descript{| Season of KDE Intern}
\location{May 2010 – Sept 2010}
\begin{tightemize}
\item Prototyped the Integration of Qt Script, Javascript scripting API into the Digikam app.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     THESIS & PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Thesis \& Publications} 
\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{p{0.05\linewidth}p{0.8\linewidth}}
2014  & 2\textsuperscript{nd}/100 teams. Amazon Internal Machine Learning Contest. (Predict Customer Support communcation method {Phone/Email} based on customer hisory). \\
2013  & \textbf{99.5 percentile}  in \href{http://www.gate.iitb.ac.in/gate2013/cs-syllabus/}{GATE 2013}. 1019\textsuperscript{th}/224160 candidates.\\
2004  & 29\textsuperscript{th}/\textasciitilde2x10\textsuperscript{5} candidates. National Talent Search Scholarship. State Level.\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{ACM Student member since 2007 and a Professional Member since 2013}.
\item Organized a workshop on “Python in Scientific Computing” led by a team from IIT Bombay and Funded by Govt. of India.
\item Regularly participated in long distance running events: Personal Best of 53mins in 10K and 2hr 20mins in a half marathon.
\end{tightemize}



\end{minipage} 
\end{document}  \documentclass[]{article}
